Parsing Postfix log files

### 2009-04-08 doc/logparser-results.tex
Wrote the section about recognition vs recognition plus processing.

% Reduce the gap between columns in tables.
\addtolength{\tabcolsep}{-1pt}

@@

XXX COMMENT THAT THE OPTIMISATION TIME HAS BEEN SPENT ON RULES, AND THAT IS
GOOD BECAUSE THAT IS WHERE THE MAJORITY OF EXECUTION TIME IS SPENT\@.
ALSO, RULE OPTIMISATION IS GENERIC, WHEREAS ACTION OPTIMISATION IS
PARSER-SPECIFIC\@.

XXX EXAMINE THE TIME SPENT RECOGNISING LOG LINES VS THE TIME SPENT
PROCESSING THEM\@.

\showgraph{build/graph-percentage-time-spent-recognising-log-lines}{XXX}{XXX}

>>>>

% Reduce the gap between columns in tables.
\addtolength{\tabcolsep}{-2pt}

@@

The optimisations described in this chapter have optimised the process of
recognising log lines, but have not affected the actions at all.  There are
two reasons for this:

    \item With the optimisations described in this chapter enabled,
        recognising log lines still dominates the execution time of the
        parser.  \Graphref{Percentage of parsing time spent recognising log
        lines graph} shows the percentage of parsing time spent recognising
        log lines for each of the \numberOFlogFILES{} log files, with mean
        and standard deviation shown in \tableref{Percentage of parsing
        time spent recognising log lines table}; for normal log files
        \input{build/include-percentage-time-spent-recognising-log-lines-mean}
        of parsing time is spent recognising log lines.  Optimal ordering
        reduces parsing time by
        \input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
        relative to shuffled ordering; processing recognised log lines
        occupies
        \input{build/include-percentage-time-spent-processing-log-lines-mean}
        of parsing time, less if using shuffled ordering, so optimising
        actions could not possibly provide as big a performance increase as
        optimally ordering rules.

    \item The process of recognising log lines is not parser-specific
        (excluding evaluation of rule conditions), so the optimisations
        described in this chapter are applicable to all parsers based on
        this architecture.  Actions are parser-specific, so it is unlikely
        that any optimisations made to actions would be portable to other
        parsers.

Individual actions or the framework could and have been optimised, but
there is plenty of existing literature on optimising programs, so the
subject will not be dealt with here.

\showgraph{build/graph-percentage-time-spent-recognising-log-lines}{Percentage
of parsing time spent recognising log lines}{Percentage of parsing time
spent recognising log lines graph}

\showtable{build/include-percentage-time-spent-recognising-log-lines-table}{Percentage
of parsing time spent recognising log lines}{Percentage of parsing time
spent recognising log lines table}
